### 2015-05-14 paper.tex
Adding alg box

%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[margin=1.25in]{geometry}

@@

@@

\subsection{Algorithm}
We'll begin by briefly discussing the intuition of the $(1 + \epsilon)$ approximation algorithm.

>>>>

%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[margin=1.25in]{geometry}

@@

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

@@

\subsection{Algorithm}

\begin{algorithm}
\caption{Cluster TODO: better name}\label{alg:cluster}
\begin{algorithmic}[1]
\Procedure{Cluster}{}
\BState \textbf{Initialization Stage:} $Q \gets Q_{init}$
\BState \textbf{Population Stage:} For $s=n, n-1, n-2, \ldots 1$ do:
\State a) Set $r=\frac{\beta OPT}{4 s}$
\State b) Remove any point $x$ such that $d(x, Q) < 2r$.
\State c) For any remaining data point $x$, denote the set of data points whose distance from $x$ is at most $r$ by $B(x, r)$.  Connect any two remaining points $a$ and $b$ if: (i) $d(a, b) \lq r$ (ii) $|B(a, r)| > \frac{s}{2}$ and (iii) $|B(b, r)| > \frac{s}{2}$.
\State d) Let $T$ be a connected component of size $ > \frac{s}{2}$.  Then i) Add $T$ to $Q$.  ii) Define the set $B(T) = \{x : d(x, y) \leq 2r$ for some $y \in T\}$.  Remove the points $B(T)$ from the instance.
\BState \textbf{Centers-Retrieving Stage}: For any choice of $k$ components $T_1, T_2, \ldots, T_k$ out of $Q$:
\State a) Find the best center $C_i$ for $T_i \cup B(T_i)$.
\State b) Partition all $n$ points according to the nearest point among the $k$ centers of the current $k$ components.
\State c) If a clustering of at most $(1 + \epsilon)OPT$ is found - output these $k$ centers and halt.
 %\hspace{\algorithmicindent} $pq.put( (v_j, e_{jk}), e_{jk}^z)$.
\EndProcedure
\end{algorithmic}
\end{algorithm}

We'll begin by briefly discussing the intuition of the $(1 + \epsilon)$ approximation algorithm.
